The limits of self commitment and private paternalism \thanks{}

### 2022-09-12 donde_old.tex
restoring comments in overlaf

We now develop the measures of net financial costs to the borrower that are used as our core pecuniary outcomes.  The two key measures are loan default, and the effective financial cost incurred by the borrower. Default is defined as losing the pawn. Let $P^c$, $P^f$, and $P^i$ the payments to principal, fees, and interest respectively. We define financial cost as the sum of payments toward the loan, plus the payment of fees, plus payments to interest, plus the appraised value of the pawn when the borrower falls into default: 
\begin{align*}
    Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
    &\quad\qquad + \underbrace{\mathds{1}(Default_i) \times Pawn \: Value_i}_{\text{Cost of losing pawn}}
\end{align*}

>>>>

We now develop the measures of net financial costs to the borrower that are used as our core pecuniary outcomes.  The two key measures are loan default, and the effective financial cost incurred by the borrower. Default is defined as losing the pawn. Let $P^c$, $P^f$, and $P^i$ the payments to principal, fees, and interest respectively. We define financial cost as the sum of payments toward the loan, plus the payment of fees, plus payments to interest, plus the appraised value of the pawn when the borrower falls into default: 
\begin{align*}
    Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
    &\quad\qquad + \underbrace{\mathds{1}(Default_i) \times Appraised \: Value_i}_{\text{Cost of losing pawn}}
\end{align*}
